A Hybrid Approach for News Recommender System using Optimization Methods

### 2021-03-12 paper/paper.tex
added summary

@@

@@

@@

@@

\section{Further research}
\label{sec:further}

@@

@@

>>>>

    Field of news recommendation has its own specific: news are getting old really fast and they don't need to be recommended.

@@

There is limited number of words, but during the day new words are being added and every night item vectors are being recalculated.

@@

User vector has same dimension as item vector.

@@

    So having all of this information allows us to tune the impact weight of each recommender using grid search.

@@

% \section{Further research}
% \label{sec:further}

@@

Recommendation system has been widely used in different areas. Collaborative filtering focuses on rating, ignoring the features of items itself. In order to better evaluate customer preference on news, we use LDA model to
calculate customer preference on news topics.

In order to forecast rating on news, we take similarity of customers and correlation between customers and news into consideration. Experiment shows that our hybrid recommendation method based on features performances better in our social media app.

What we contribute is we proposed a new hybrid recommendation method based on features to improve the performance.

@@

We use the average method to set the weight to adjust the predicted rating in this article, whose rationality needs to be further improved. Moreover, our method has yet to be tested on other data sets for its performance.
